---
title: "Practice SQL"
author: "Gloria Baidoo"
date: "2024-10-12"
output: pdf_document
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
#install.packages("duckdb")
#install.packages("DBI")
#install.packages("nycflights13")
```

```{r pressure, echo=FALSE}
library(duckdb)
library(DBI)
library(tidyverse)
library(nycflights13)
```

```{r}
con <- dbConnect(duckdb(dbdir = "../data/flights.duckdb", read_only = TRUE))
```

```{sql connection=con}
SHOW TABLES;
```

```{sql connection=con}
DESCRIBE;
```

# Practice 1: Practice 1: Select Flights from a Specific Carrier 

```{sql connection=con}
SELECT *
FROM flights
WHERE carrier = 'UA';
```

# Practice 2: Count the Number of Flights for Each Carrier
```{sql connection=con}
SELECT carrier, COUNT(*) AS flight_count
FROM flights
GROUP BY carrier;
```

# Practice 3: Find the Flights with the Longest Distance
```{sql connection=con}
SELECT *
FROM flights
ORDER BY distance DESC
LIMIT 10;
```

# Practice 4: Calculate Average Arrival Delay for Each Carrier
```{sql connection=con}
SELECT carrier, AVG(arr_delay) AS avg_arrival_delay
FROM flights
WHERE arr_delay IS NOT NULL
GROUP BY carrier;
```

# Practice 5: Find Flights Departing from JFK to LAX
```{sql connection=con}
SELECT *
FROM flights
WHERE origin = 'JFK' AND dest = 'LAX';
```

# Practice 6: Calculate the Total Number of Flights Each Month
```{sql connection=con}
SELECT month, COUNT(*) AS total_flights
FROM flights
GROUP BY month
ORDER BY month;
```

# Practice 7: Find Flights with Departure Delays Greater than 2 Hours
```{sql connection=con}
SELECT *
FROM flights
WHERE dep_delay > 120;

```

# Practice 8: Find the Number of Flights per Day
```{sql connection=con}
SELECT year, month, day, COUNT(*) AS total_flights
FROM flights
GROUP BY year, month, day
ORDER BY year, month, day;
```

# Practice 9: Find Flights That Arrived Early
```{sql connection=con}
SELECT *
FROM flights
WHERE arr_delay < 0;
```

# Practice 10: Find the Average Air Time per Carrier
```{sql connection=con}
SELECT carrier, AVG(air_time) AS avg_air_time
FROM flights
WHERE air_time IS NOT NULL
GROUP BY carrier;
```

